History of Social Work Research: Data Cleaning

### 2015-02-03 dataCleaning.Rmd
Working on data cleaning.

# Set the working directory
setwd("/Users/beperron/Git/SocialWorkResearch/Data")
```

@@

The articles were reviewed and a first round of exclusions were made.

```{r}
exclusions <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "Hospital Social Service",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Learning Disabilities Research & Practice",
    "New York State Department of Social Welfare, Division Publication",
    "Pennsylvania Social Work",
    "Proceedings of the National Converence of Social Work",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Work Technique",
    "Social Work Today", # Magazine
    "Social Work Yearbook",
    "The New Social Worker",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "University of Chicago Social Service Monograph",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor",
    "University of Chicago Social Service Monograph")
ebsco.remove <- full.df[full.df$record %in% exclusions, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]

@@

>>>>

# Set the working directory
setwd("/Users/beperron/Git/SocialWorkResearch/Data")

# Strip leading and trailing white-space on all records
full.df$record <- stringr::str_trim(full.df$record, side = "both")
```

@@

The articles were reviewed and a first round of exclusions were made.  All decisions to exclude were based on group consenus.

```{r}
exclusions <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "Hospital Social Service",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Learning Disabilities Research & Practice",
    "New York State Department of Social Welfare, Division Publication",
    "Pennsylvania Social Work",
    "Proceedings of the National Converence of Social Work",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Work Technique", 
    "Social Work Today", 
    "Social Work Yearbook", 
    "The New Social Worker",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "University of Chicago Social Service Monograph",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor",
    "University of Chicago Social Service Monograph")

ebsco.remove <- full.df[full.df$record %in% exclusions, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]

@@

```{r}
full.df$record <- ifelse(full.df$record == 
    "Eugenics and Social Welfare Bulletin",     # Spelling difference
    "Eugenics & Social Welfare Bull.",          # Spelling difference
                    full.df$record)

full.df$record <- ifelse(full.df$record == 
    "The British Journal of Social Work",       # Old name
    "British Journal of Social Work",           # New name
                    full.df$record)

full.df$record <- ifelse(full.df$record == 
    "Social Work & Social Sciences Review",     # Spelling difference
    "Social Work and Social Sciences Review",   # Spelling difference
                    full.df$record)

full.df$record <- ifelse(full.df$record == 
    "Social Work with Groups",                  # Spelling difference
    "Social Work With Groups",                  # Spelling difference
                    full.df$record)

full.df$record <- ifelse(full.df$record == 
    "Computers in Human Services",              # Old name
    "Journal of Technology in Human Services",  # New name 
                    full.df$record)

full.df$record <- ifelse(full.df$record == 
    "Journal of Sociology & Social Welfare",    # Spelling difference
    "Journal of Sociology and Social Welfare",  # Spelling difference
                    full.df$record)

full.df$record <- ifelse(full.df$record == 
    "The Family" | full.df$record ==                   # Old name
    "Journal of Social Casework" | full.df$record ==    # Old name
    "Social Casework",                                  # Old name
    "Families in Society",                              # New name
                    full.df$record)

full.df$record <- ifelse(full.df$record == 
    "Social Work in Education",                 # Old name
    "Children & Schools",                       # New name
                    full.df$record)

full.df$record <- ifelse(full.df$record == "Contemporary Rural Social Work (Electronic only) ", 
                        "Contemporary Rural Social Work (Electronic only) ", full.df$record)
